---
title: "for loops"
author: "Tim Covino"
date: "2023-03-30"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(dataRetrieval)

```

You could type out the sites and names or you could pull it from some whatNWISsites call. 
```{r}
sites <- c("06037500", "12363000")
names <- c("salmon", "flathead")
params <- c("00060", "00010") # This is temperature and Q. You can obviously change and then also change the readNWISdata to something else and the parameters, etc. 
start <- as_date("1900-10-01") # Just a nice round number for start time. 
end <- as_date("2022-09-30") #End of last water year. 
service <- "dv" # Daily values

# Removed those sites for testing
# "12363000", "13296000", "12344000", "12447200", "13331500", "06191500"

```

Instead of writing a function, we use for(i in sites). So this will run through the list of sites and download the data and do whatever else you tell it. Then we create a filename that is data_, i. So it will write out data_06037500.csv for the first, data_12363000.csv for the second, so on. Then I just read the .csv in to check and make sure it worked.

```{r}
for (i in sites) {
  tmp <- readNWISdata(sites = i, parameterCd = params, service = service, startDate = start, endDate = end) %>% 
    renameNWISColumns()
  filename <- paste("data_", i, sep="")
  write_csv(tmp, file = paste(filename, ".csv", sep=""))
}

test_df <- read_csv("data_06037500.csv")
```


Here, I've added a second for. For i in sites and for j in names. So when we get to the naming we look to the j for the name to put that in the title of the .csv
```{r}
for (i in sites) {
  for (j in names) {
  tmp <- readNWISdata(sites = i, parameterCd = params, service = service, startDate = start, endDate = end) %>% 
    renameNWISColumns()
  filename <- paste("data_", j, sep="")
  write_csv(tmp, file = paste(filename, ".csv", sep=""))
  }
}

test_df <- read_csv("data_salmon.csv")

library(readr)

list_of_files <- list.files(path = "/Users/timothycovino/Dropbox/classes/ensc_445/skills_tutorial",
                            recursive = TRUE,
                            pattern = "\\.csv$",
                            full.names = TRUE)

df <- readr::read_csv(list_of_files, id = "file_name")
```


```{r}
for (i in sites) {
  for (j in names) {
  tmp <- readNWISdata(sites = i, parameterCd = params, service = service, startDate = start, endDate = end) %>% 
    renameNWISColumns()
  assign(paste("data_", j, sep=""), tmp)
  rm(tmp) 
  }
}
```

```{r}
testFunction_2 <- function() {      
  out_list <- vector(mode = "list", length = 5)       
  for (i in 1:5)  {        
    x <- data.frame(c(1:10), c(1,2,3,4,5,6,7,8,9,10), c(10:19))        
    out_list[[i]] <- x 
    names(out_list)[i] <- paste("name", i, sep = "_")       
  }
  return(out_list)
}

test_list <- testFunction_2()
```

```{r}
df <- tibble::tibble(
  a = rnorm(10),
  b = rnorm(10),
  c = rnorm(10),
  d = rnorm(10)
)

x <- df$a
rng <- range(x, na.rm = TRUE)



```



