---
title: "ggsave"
author: "Tim Covino"
date: "2023-04-05"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
library(tidyverse)
```

Make data frame. 
```{r}
df_x <- c(1, 3, 2, 5, 4, 6)
df_y <- c(9, 4, 5, 3, 6, 5)
df <- cbind(df_x, df_y) %>% 
  as_tibble()
```

Make plot. 
```{r}
my_plot <- df %>% 
  ggplot(aes(x = df_x, y = df_y)) +
  geom_point()

my_plot
```

Save plot. You can adjust all these things. The dpi. The height and the width. You can also just see what the default settings give you. You can also save as other file types like "eps", "jpeg", "tiff", whatever. 

When you save this it will put it in whatever directory you are working in. So if you are using an R project that will be the folder the figure will be saved in. You can also change this with path. 
```{r}
ggsave(filename = "my_plot.png", device = "png", plot = my_plot, width = 5, height = 5, units = "in", dpi = 400)
```

So, for example, say I wanted to make another folder in my project folder called figs for my figures and put all my figures in there, I could do the following. 
```{r}
ggsave(filename = "my_plot.png", device = "png", plot = my_plot, width = 5, height = 5, units = "in", dpi = 400, path = "figs")
```





